State of the Art in Scientific Workflow Systems

### 2014-05-27 paper.tex
pegasus desc

Large scale workflows from astronomy, biology, and high-energy physics have
been shown to run via Pegasus on distributed computing resources such as
clusters, Grids and supercomputers.  Recent developments in Pegasus enables it
to run workflows on cloud environments~\cite{peg-cloud}. Pegasus system is
known to be extendible as illustrated by a recent integration
effort~\cite{peg-hubzero} between Pegasus and the Hubzero
portal~\cite{hubzero}.

>>>>

Large scale workflows from astronomy, biology, and high-energy physics have
been shown to run via Pegasus on distributed computing resources such as
Clusters, Grids and Supercomputers.  Recent developments in Pegasus enables it
to run workflows on cloud environments~\cite{peg-cloud}. Pegasus system is
known to be extendible as illustrated by a recent integration
effort~\cite{peg-hubzero} between Pegasus and the Hubzero
portal~\cite{hubzero}.
